% !TEX program = xelatex

\documentclass[]{sumbal-resume}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\usepackage{tikz}
\usepackage{verbatim}
\begin{document}

\firstname{Abdullah} 
\lastname{Sumbal}
\phone{(514) 967-6626}
\email{abdullahsumbal@gmail.com}
\website{abdullahsumbal.com}
\github{abdullahsumbal} 
\header

% \hspace*{-\parindent}%
%\begin{minipage}[t]{0.33\textwidth}
% \begin{minipage}[t]{0.66\textwidth}

% \resizebox{0.628\textwidth}{!}{
% \newcommand\logoheight{3.19}
% \begin{tikzpicture}[line width=2mm, line cap=round, draw opacity = 0.7]
% \draw (-1, 0) -- (-2, \logoheight);
% \draw (1, 0) -- (2, \logoheight);
% \draw [accent] (-1, 0) -- (0, \logoheight);
% \draw [accent] (1, 0) -- (0, \logoheight);
% \end{tikzpicture}
% }~\\

% \vspace{0.26cm}






\section{Education}{}
\noindent\project{McGill University}{Software Engineering (GPA: 3.6 / 4.0)}{2020 January}
\sectionsep

\section{Skills}
\subsection{Languages}
%\subsectionBlue{Languages}
\normalfont{Python \tb Java \tb C \tb SQL \tb C++ \tb Bash \tb JavaScript  \tb HTML \tb CSS \\}
\vspace{2pt}\subsection{Framework \& Libraries}
\normalfont{Spring \tb Bootstrap \tb Node.js \tb Express.js \tb  React \tb Flask \tb Scikit-learn \tb QT \tb VHDL \tb \LaTeX \tb TensorFlow \tb Logback\\}
\vspace{2pt}\subsection{Tools}
\normalfont{Git \tb Linux \tb Docker \tb  OpenShift \tb Maven \tb Gradle \tb Jira \tb Firebase \tb CI/CD \tb Udeploy \tb Jenkins \tb TeamCity \\}
\sectionsep

\section{Experience \& Research}

\project{Software Developer - AVP}{Citi Bank}{March 2020 - Present}
%\vspace{\topsep}
\begin{tightemize}
\item Develop Citi's digital marketplace for APIs for internal and external customers.
\item Addressed priority production bugs and improvements in Java Spring Boot API REST services. 
\item Containerized applications and automated build pipelines (CI/CD) using Jenkins and OpenShift.
\item Managed employee training for all new recruits and offered continuous guidance and mentorship on best practices.
\end{tightemize}
	
\project{GIS Web Developer}{IHSP}{Jan 2019 - April 2021}
%\vspace{\topsep}
\begin{tightemize}
\item Optimized web services performance by $50 \%$ for \href{http://lifesatisfaction.ca}{lifesatisfaction.ca} using open source technologies.
\item Developed data load process to generate and host vector tiles for current and future projects.
\end{tightemize}

\project{Research Assistant}{Faculty of Medicine}{May 2019 - Aug 2019}

\begin{tightemize}
\item Developed a prediction model to distinguish between various voice types using Machine Learning algorithms. 
\item Performed analysis on the impact of voice fatigue on running speech using a neck surface accelerometer.
\end{tightemize}


\project{Software Intern}{General Electric}{Sep 2016 - Dec 2017}
\begin{tightemize}
\item Improved team productivity by designing automation tools for regression testing. 
\item Discovered critical issues by redesigning the database validation system which prevented product recall.
\item Developed tools to aid the team in visualizing the communication tree between nodes.
\end{tightemize}

\sectionsep

\section{Projects}

\projectsumbal{\mygithub{data-analysis}[Battery Data Analysis]} \\
\descriptproject{Python | PyQt}
\begin{tightemize}
\item Developed data analysis plotting tools for the Chemistry Department at McGill University which will aid in chemical battery research for the next $20 \ years$. 
\item Designed an interface which allows data communication between a pH meter and the experiment apparatus. 
\end{tightemize}

\projectsumbal{\mygithub{capstoneproject}[3D Visualization of human Spine]} \\
\descriptproject{Python | PyQt}
\begin{tightemize}
\item Developed a desktop application for rendering the human spine by combining X-Ray, MRI and surface topography to facilitate in surgery. 
\end{tightemize}

\projectsumbal{\mygithub{spin-bike-dashboard}[Remote PC Shutdown automation]} \\
\descriptproject{Python | React | Authentication }
\begin{tightemize}
\item Developed an application to remotely shutdown using Firebase services and Python QT application
\end{tightemize}

\projectsumbal{\mygithub{SSD_Tracker}[SSD Tracker]} \\
\descriptproject{C++ | Caffe}
\begin{tightemize}
\item Developed an application to count, detect and track objects in a video stream in real-time running at $30 \ frames/sec$ using single shot multi-box detector deep learning algorithm.
\end{tightemize}


\begin{comment}
\section{Open Source}
\subsection{Other Projects}
\content{\href{https://github.com/abdullahsumbal}{github.com}}
% \githublink{abdullahsumbal}{McGillTour}{McGill Tour} 
\pair{Sprawl Website}{Street Network} \\
\pair{\githublink{abdullahsumbal}{Voice-Segmentation/tree/master/code/monitor}{Sound Monitor}}{Label Cough time} \\
\pair{\githublink{abdullahsumbal}{McGillTour}{McGill Tour}}{Building Path Finder} \\ 
\pair{\githublink{abdullahsumbal}{Hamza_Gift}{Squash}}{Website Game Tracker} \\
\pair{\githublink{abdullahsumbal}{Find-Keywords}{Keywords}}{Website Keyword Finder} \\
\pair{\githublink{abdullahsumbal}{data-analysis}{Data Analysis}}{Combi Cell Plotter} \\
\pair{\githublink{abdullahsumbal}{mvc_template}{MVC}}{Software Architecture } \\
\pair{\githublink{abdullahsumbal}{Augmented-Reality-Unity}{AR}}{AR Unity Games} \\
%\end{minipage}
\hfill
%\begin{minipage}[t]{0.66\textwidth}
\section{Experience \& Research}

\project{GIS Web Developer}{IHSP}{Jan 2019 - Present}
\vspace{\topsep}
\begin{tightemize}
\item Optimized web services performance by $50 \%$ for \href{http://lifesatisfaction.ca}{lifesatisfaction.ca} using open source technologies.
\item Developed a pipeline for generating and hosting vector tiles for current and future projects.
\end{tightemize}

\project{Research Assistant}{Faculty of Medicine}{May 2019 - Aug 2019}

\begin{tightemize}
\item Developed a prediction model to distinguish between various voice types using Machine Learning algorithms. 
\item Performed analysis on the impact of voice fatigue on running speech using a neck surface accelerometer.
\end{tightemize}


\project{Software Intern}{General Electric}{Sep 2016 - Dec 2017}
\begin{tightemize}
\item Improved team productivity by designing automation tools for regression testing. 
\item Discovered critical issues by redesigning the database validation system which prevented product recall.
\item Developed tools to aid the team in visualizing the communication tree between nodes.
\end{tightemize}

\sectionsep
\end{comment}

%\end{minipage}
\end{document}

